A Systematic Literature Review on Extensions to Role-Based Access Control

### 2014-02-09 paper/sections/categorization.tex
Adding back analysis section and cleaning up.

Based on data extracted from the primary sources and the English definitions for each noun-phrase we provide a definition for each observed model category. 
Some category descriptors contain abbreviations in parenthesis that match the shortened name found within Appendix A \ref{tab:categorization} which presents each primary source within it's designated category.

@@

The 27 primary sources produced a set of eight hierarchical categories. Table \ref{tab:categorization} summarizes each primary source under their designated category and furthermore, displays the perceived hierarchy of the categories. Figure~\ref{fig:category_structrure} shows the hierarchy structure among categories. The Constraint, Organizational, Privacy, Task, and Spatial and Temporal categories can be special cases of the Context category. The Spatio-Temporal category subsumes Spatial and Temporal categories. The Spatial and Temporal categories were treated as subsets of the broader category of Spatio-Temporal since this category encompasses them individually and the Spatio-Temporal category contained more primary sources that the Spatial or Temporal categories alone.

When looking across all categories, we noted that each category added domain specific features on top of the RBAC Reference Model.
These domain specific features were under the surface these features adding contextual relationships between the core user, permission and role entities.  Thus, we
concluded that all categories stemmed from the context category, of which some primary sources were already deemed direct members.

>>>>

We provide a definition for each observed model category based on data extracted from the primary sources and the English definitions for each noun-phrase.
Some category descriptors contain abbreviations in parenthesis that match the shortened name found within Appendix 1 \ref{tab:categorization} which presents each primary source within it's designated category.

@@

The 27 primary sources produced a set of eight hierarchical categories. 
Table \ref{tab:categorization} summarizes each primary source under their designated category and furthermore, displays the perceived hierarchy of the categories. 
Figure~\ref{fig:category_structrure} shows the hierarchy structure among categories. 
The Constraint, Organizational, Privacy, Task, and Spatial and Temporal categories can be special cases of the Context category. 
The Spatial and Temporal categories were treated as subsets of the broader category of Spatio-Temporal since this category encompasses them individually and the Spatio-Temporal category was derived from primary sources directly.

When looking across all categories, we noted that each category added specific features on top of the RBAC Reference Model.
These features were under the surface adding contextual relationships between the core user, permission and role entities. 
Thus, we concluded that all categories stemmed from the context category, of which some primary sources were already deemed direct members.

### 2014-02-09 paper/sections/process.tex
Updating data display tables.
Adding back analysis section and cleaning up.

\begin{table}
\centering
\caption{Paper counts after applying search strategy}
\begin{tabular}{|p{3.5cm}|p{1.25cm}|p{4.25cm}|p{4.25cm}|p{1cm}|}

@@

The title elimination round resulted in Reviewer 1 selecting 305 papers, and Reviewer 2 selecting 176 papers with 149 papers of overlap between the two. 
Between the two reviewers selections, there were 332 papers not in common, of which, 149 were rejected and 141 retained after a second review.

@@

The abstract elimination round resulted in Reviewer 1 selecting 86 papers, and Reviewer 2 selecting 102 papers with 51 papers of overlap between the two. 
Between the two reviewers selections, there were 137 papers not in common, of which, 116 were rejected and 21 retained after a second review.

@@

\begin{table}
\centering
\caption{Elimination Rounds}
\begin{tabular}{ c c | c | c | c | }
\cline{3-5}

>>>>

\begin{table}
\centering
\caption{Paper counts after applying search strategy}
\vspace{0.1 in}
\begin{tabular}{ | l | r | r | r | r | }

@@

The title elimination round resulted in Reviewer 1 selecting 305 papers, and Reviewer 2 selecting 176 papers with 149 papers of overlap between the two. 
There were 332 papers found not to be in common, of which, 149 were rejected and 141 retained after a second review.

@@

The abstract elimination round resulted in Reviewer 1 selecting 86 papers, and Reviewer 2 selecting 102 papers with 51 papers of overlap between the two. 
There were 137 papers found not to be in common, of which, 116 were rejected and 21 retained after a second review.

@@

\begin{table}
\centering
\caption{Elimination Rounds}
\vspace{0.1 in}
\begin{tabular}{ l l | r | r | r | }
\cline{3-5}
